Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
Update A3-Pt1.Rmd

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        # YOUR CODE HERE
    )

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE

ice_extent_yearly
```

>>>>

```{r cyclones_data_update_2, error=TRUE}
cyclones_data_update_2 <- cyclones_data_update_1 |>
    mutate(
        date = make_datetime(ObservYear, Month, Day, Hour * 100 + Minute)
    )

@@

```{r}
ice_extent_yearly <- ice_extent_daily |>
    # YOUR CODE HERE
    group_by(year, region) |>
    summarize(
        min = min(ice_extent, na.rm = TRUE),
        max = max(ice_extent, na.rm = TRUE),
        .groups = "drop"
    ) |>
    pivot_longer(
        cols = c("min", "max"),
        names_to = "name",
        values_to = "value"
    )
ice_extent_yearly
```
